Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-09 Paper/ms.tex
A few more refs

In previous studies, the inference was performed by doing separate runs, one
for each possible value of $N$, and calculating the marginal likelihood
$p(\boldsymbol{D} | N)$ as a function of $N$.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Hou, Goodman, 
\& Hogg}{2014}]{fengjo} Hou F., Goodman J., Hogg D.~W., 2014, arXiv, arXiv:1401.6128

>>>>

The number of orbiting planets, $N$, is usually of significant interest.
Most authors have carried out the inference for $N$ by doing separate runs, one
for each possible value of $N$, and calculating the marginal likelihood
$p(\boldsymbol{D} | N)$ as a function of $N$
\citep[e.g.][]{2011MNRAS.415.2523G, 2014MNRAS.437.3540F, fengji}.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Feroz 
\& Hobson}{2014}]{2014MNRAS.437.3540F} Feroz F., Hobson M.~P., 2014, MNRAS, 437, 3540

\bibitem[\protect\citeauthoryear{Gregory}{2011}]{2011MNRAS.415.2523G} 
Gregory P.~C., 2011, MNRAS, 415, 2523

\bibitem[\protect\citeauthoryear{Hou, Goodman, 
\& Hogg}{2014}]{fengji} Hou F., Goodman J., Hogg D.~W., 2014, arXiv, arXiv:1401.6128
